XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-27 talk/icooolps2011/paper.tex
reworded something and fixed a typo

One of the hardest parts of implementing a dynamic language efficiently is to
optimize its object model. This is made harder by the fact that many recent
languages such as Python, JavaScript or Ruby have rather complex core object
semantics. For them, implementing just an interpreter is already an arduous
\pedronis{XXX ardous seems a bit too strong} task. Implementing them efficiently with a just-in-time compiler (JIT) is
extremely challenging, because or their many corner-cases.

>>>>

One of the hardest parts of implementing a dynamic language efficiently is to
optimize its object model. This is made harder by the fact that many recent
languages such as Python, JavaScript or Ruby have rather complex core object
semantics. For them, implementing just an interpreter is already a complex
task. Implementing them efficiently with a just-in-time compiler (JIT) is
extremely challenging, because of their many corner-cases.
